ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
Edited activie vision systyem

The work we present in this paper is an advancement towards the ActiVis projects larger goal of developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
This work focuses on guiding a user towards an object in one, static environment and is limited to 2 dimensions (pan and tilt).

@@

In this case, the error is defined as the difference between the desired object and the object currently within view. 
The implication of this modification is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to take be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}

Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates. 
In our previous work, we assumed a `perfect classifier' and solved the problem using a plain Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and implement a POMDP that can better handle the observation uncertainties inherent to modern object detectors and classifiers. 
The design of the human controller is discussed next.

>>>>

The ActiVis project's goal is developing a stand-alone mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).

@@

In this case, the error, $e$, is defined as the difference between the desired object and the object currently within view. 
The implication of adding a human into the loop is that an additional block, \emph{H}, is added to simulate a human that receives an control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge with people is that a person may interpret \emph{u} in any unpredictable way (i.e.\ apply a transformation) that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
%These design considerations are addressed in previous work. \todo{how to state that we designed the interface already if its unpublished?}

Another fact to take note of is the measurement noise, \emph{n}, added in the feedback loop that simulates an object detector making classification errors that will influence the action that \emph{K} generates. 
In our previous work, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and implement a POMDP that can handle observation uncertainties in object detectors and classifiers.
